---
title: "Plotting scripts for V. mimicus paper"
output: html_document
date: "2026-06-11"
---
Load required libraries, including most recent version of ggplot2 

```{r load required libraries, warning = F, results = 'hide', error = F, message = F}
knitr::opts_chunk$set(warning = FALSE, message = FALSE) 
install.packages("ggplot2", repos = "http://cran.us.r-project.org")
library(tidyverse)
library(ggplot2)
library(tidyverse)
library(svglite)
library(cowplot)
library(ggtree)
library(phytools)
library(ggtreeExtra)
library(ggnewscale)
library(aplot)
library(paletteer)
```

Read phylogenetic tree nwk file and all associated metadata 
``` {r read tree and metadata}
# read tree 
mimicus_tree <- read.tree("iqtree_mimicus_contree.nwk")
# root on most basal genome/ most closely related to metoecus 
rooted_tree <- root(mimicus_tree, outgroup = "GCA_000176415.1_ASM17641v1_genomic", resolve.root = TRUE)

# rename tree tips 
## function to remove extra bits of name 
simplify_label <- function(label) {
  sub("^([A-Z]{3}_[0-9]+\\.[0-9]+).*", "\\1", label)
}
## rename tips 
rooted_tree$tip.label <- sapply(rooted_tree$tip.label, simplify_label)

# visualise rooted tree
p <- ggtree(rooted_tree)

# read baps partitions
## fastbaps was run on cluster with optimise.baps as prior and using phylogeny
optimise.baps <- read_table("mimicus_n161_baps_optimise_baps.tsv")
optimise.baps <- optimise.baps[,1:2]
## rename sample ids and col headers
optimise.baps[1] <- sapply(optimise.baps[1], simplify_label)
names(optimise.baps) <- c("id", "level")

# read in metadata for public mimicus genomes 
mimicus_metadata <- read.csv("mimicus_metadata_v4.csv")
rownames(mimicus_metadata) <- mimicus_metadata$id
mimicus_metadata <- mimicus_metadata[,-(2)]
## NAs for missing values 
mimicus_metadata[mimicus_metadata == ""] <- NA
mimicus_metadata[mimicus_metadata == "not collected"] <- NA

# merge metadata and BAPS cluster for all mimicus genomes (n = 161)
mimicus_metadata_baps <- merge(optimise.baps, mimicus_metadata)

# read abricate - CARD
mimicus_card <- data.frame(read_table("mimicus_summary_card.tsv"))
rownames(mimicus_card) <- mimicus_card$FILE
mimicus_card <- mimicus_card[, -1]
rownames(mimicus_card) <- sapply(rownames(mimicus_card), simplify_label)
## pivot longer for heatmap plotting 
mimicus_card_long <- mimicus_card %>%
  as.data.frame() %>%
  rownames_to_column("id") %>%
  pivot_longer(
    cols = -id,
    names_to = "gene",
    values_to = "presence"
  )

# read abricate - VFDB 
mimicus_vfdb <- read.csv("mimicus_n161_abricate_vfdb_plotting.csv")
rownames(mimicus_vfdb) <- mimicus_vfdb$X_FILE
mimicus_vfdb <- mimicus_vfdb[, -1]
rownames(mimicus_vfdb) <- sapply(rownames(mimicus_vfdb), simplify_label)
## pivot longer for heatmap plotting 
mimicus_vfdb_long <- mimicus_vfdb %>%
  as.data.frame() %>%
  rownames_to_column("id") %>%
  pivot_longer(
    cols = -id,
    names_to = "gene",
    values_to = "presence"
  )

# get tip coordinates to mark tips of samples from this study 
tip_coords <- p$data %>%
  filter(isTip) %>%
  select(label, x, y)
names(tip_coords) <- c("id", "xcoord", "ycoord")
## merge with metadata 
mimicus_metadata_baps_tips <- left_join(tip_coords, mimicus_metadata_baps, by = "id")

## ctxB allele data 
mimicus_ctxB_alleles <- read_table("mimicus_ctxB_alleles_assigned.tsv")
mimicus_ctxB_alleles$id <- sapply(mimicus_ctxB_alleles$id, simplify_label)

mimicus_metadata_baps_tips <- merge(mimicus_ctxB_alleles, mimicus_metadata_baps_tips, by = "id", all.y = T)

## bangladesh genomes province 
mimicus_province <- read_csv("mimicus_bangladesh_state.csv")
mimicus_metadata_baps_tips_province <- merge(mimicus_province, mimicus_metadata_baps_tips, by = "id", all.y = T)

# colours for plotting
baps_colours <- c("1" = "#FBE183", "2" = "#F4C40F", "3" = "#FE9B00", "4" = "#D8443C", "5" = "#9B3441", "6" = "#DE597C", "7"= "#E87B89", "8" = "#E6A2A6", "9" = "#AA7AA1", "10" = "#9F5691", "11" = "#633372", "12" = "#1F6E9C", "13" = "#2B9B81", "14" = "#92C051", "15" = "#72874E", "16" = "#A08018", "17" = "#307808", "18" = "#484880", "19"= "#68A8E0", "20" = "#CD8A56", "21" = "#FF1494", "22" = "#417BA1")

```

Get node ID for MRCA in each BAPS lineage as defined above
``` {r get node for MRCA for each lineage}

### get tip names per node per baps level

node_l1_tips <- mimicus_metadata_baps_tips[mimicus_metadata_baps_tips$level == 1,]$id
node_l1 <- MRCA(p, node_l1_tips)

node_l2_tips <- mimicus_metadata_baps_tips[mimicus_metadata_baps_tips$level == 2,]$id
node_l2 <- MRCA(p, node_l2_tips)

node_l3_tips <- mimicus_metadata_baps_tips[mimicus_metadata_baps_tips$level == 3,]$id
node_l3 <- MRCA(p, node_l3_tips)

node_l4_tips <- mimicus_metadata_baps_tips[mimicus_metadata_baps_tips$level == 4,]$id
node_l4 <- MRCA(p, node_l4_tips)

node_l5_tips <- mimicus_metadata_baps_tips[mimicus_metadata_baps_tips$level == 5,]$id
node_l5 <- MRCA(p, node_l5_tips)

node_l6_tips <- mimicus_metadata_baps_tips[mimicus_metadata_baps_tips$level == 6,]$id
node_l6 <- MRCA(p, node_l6_tips)

node_l7_tips <- mimicus_metadata_baps_tips[mimicus_metadata_baps_tips$level == 7,]$id
node_l7 <- MRCA(p, node_l7_tips)

node_l8_tips <- mimicus_metadata_baps_tips[mimicus_metadata_baps_tips$level == 8,]$id
node_l8 <- MRCA(p, node_l8_tips)

node_l9_tips <- mimicus_metadata_baps_tips[mimicus_metadata_baps_tips$level == 9,]$id
node_l9 <- MRCA(p, node_l9_tips)

node_l10_tips <- mimicus_metadata_baps_tips[mimicus_metadata_baps_tips$level == 10,]$id
node_l10 <- MRCA(p, node_l10_tips)

node_l11_tips <- mimicus_metadata_baps_tips[mimicus_metadata_baps_tips$level == 11,]$id
node_l11 <- MRCA(p, node_l11_tips)

node_l12_tips <- mimicus_metadata_baps_tips[mimicus_metadata_baps_tips$level == 12,]$id
node_l12 <- MRCA(p, node_l12_tips)

node_l13_tips <- mimicus_metadata_baps_tips[mimicus_metadata_baps_tips$level == 13,]$id
node_l13 <- MRCA(p, node_l13_tips)

node_l14_tips <- mimicus_metadata_baps_tips[mimicus_metadata_baps_tips$level == 14,]$id
node_l14 <- MRCA(p, node_l14_tips)

node_l15_tips <- mimicus_metadata_baps_tips[mimicus_metadata_baps_tips$level == 15,]$id
node_l15 <- MRCA(p, node_l15_tips)

node_l16_tips <- mimicus_metadata_baps_tips[mimicus_metadata_baps_tips$level == 16,]$id
node_l16 <- MRCA(p, node_l16_tips)

node_l17_tips <- mimicus_metadata_baps_tips[mimicus_metadata_baps_tips$level == 17,]$id
node_l17 <- MRCA(p, node_l17_tips)

node_l18_tips <- mimicus_metadata_baps_tips[mimicus_metadata_baps_tips$level == 18,]$id
node_l18 <- MRCA(p, node_l18_tips)

node_l19_tips <- mimicus_metadata_baps_tips[mimicus_metadata_baps_tips$level == 19,]$id
node_l19 <- MRCA(p, node_l19_tips)

node_l20_tips <- mimicus_metadata_baps_tips[mimicus_metadata_baps_tips$level == 20,]$id
node_l20 <- MRCA(p, node_l20_tips)

node_l21_tips <- mimicus_metadata_baps_tips[mimicus_metadata_baps_tips$level == 21,]$id
node_l21 <- MRCA(p, node_l21_tips)

node_l22_tips <- mimicus_metadata_baps_tips[mimicus_metadata_baps_tips$level == 22,]$id
node_l22 <- MRCA(p, node_l22_tips)

## make data frame of tip labels per node

df_n1 <- data.frame(node_l1_tips, node_l1)
names(df_n1) <- c("id", "clade_node")

df_n2 <- data.frame(node_l2_tips, node_l2)
names(df_n2) <- c("id", "clade_node")

df_n3 <- data.frame(node_l3_tips, node_l3)
names(df_n3) <- c("id", "clade_node")

df_n4 <- data.frame(node_l4_tips, node_l4)
names(df_n4) <- c("id", "clade_node")

df_n5 <- data.frame(node_l5_tips, node_l5)
names(df_n5) <- c("id", "clade_node")

df_n6 <- data.frame(node_l6_tips, node_l6)
names(df_n6) <- c("id", "clade_node")

df_n7 <- data.frame(node_l7_tips, node_l7)
names(df_n7) <- c("id", "clade_node")

df_n8 <- data.frame(node_l8_tips, node_l8)
names(df_n8) <- c("id", "clade_node")

df_n9 <- data.frame(node_l9_tips, node_l9)
names(df_n9) <- c("id", "clade_node")

df_n10 <- data.frame(node_l10_tips, node_l10)
names(df_n10) <- c("id", "clade_node")

df_n11 <- data.frame(node_l11_tips, node_l11)
names(df_n11) <- c("id", "clade_node")

df_n12 <- data.frame(node_l12_tips, node_l12)
names(df_n12) <- c("id", "clade_node")

df_n13 <- data.frame(node_l13_tips, node_l13)
names(df_n13) <- c("id", "clade_node")

df_n14 <- data.frame(node_l14_tips, node_l14)
names(df_n14) <- c("id", "clade_node")

df_n15 <- data.frame(node_l15_tips, node_l15)
names(df_n15) <- c("id", "clade_node")

df_n16 <- data.frame(node_l16_tips, node_l16)
names(df_n16) <- c("id", "clade_node")

df_n17 <- data.frame(node_l17_tips, node_l17)
names(df_n17) <- c("id", "clade_node")

df_n18 <- data.frame(node_l18_tips, node_l18)
names(df_n18) <- c("id", "clade_node")

df_n19 <- data.frame(node_l19_tips, node_l19)
names(df_n19) <- c("id", "clade_node")

df_n20 <- data.frame(node_l20_tips, node_l20)
names(df_n20) <- c("id", "clade_node")

df_n21 <- data.frame(node_l21_tips, node_l21)
names(df_n21) <- c("id", "clade_node")

df_n22 <- data.frame(node_l22_tips, node_l22)
names(df_n22) <- c("id", "clade_node")

clade_nodes <-rbind(df_n1, df_n2, df_n3, df_n4, df_n5, df_n6,
      df_n7, df_n8, df_n9, df_n10, df_n11, df_n12,
      df_n13, df_n14, df_n15, df_n16, df_n17, df_n18, 
      df_n19, df_n20, df_n21, df_n22)

mimicus_metadata_baps_tips <- merge(clade_nodes, mimicus_metadata_baps_tips, by = "id")

```

Plot phylogenetic tree with clades coloured by BAPS cluster
``` {r highlight clades}
# add column for colour based on baps cluster
mimicus_metadata_baps_tips$fill_col <-
  baps_colours[as.character(mimicus_metadata_baps_tips$level)]

# plot tree and colour by baps cluster 
p0 <- p + geom_hilight(node = mimicus_metadata_baps_tips$clade_node, fill = mimicus_metadata_baps_tips$fill_col, extendto = 0.29, alpha = 0.1, colour =  mimicus_metadata_baps_tips$fill_col) + geom_tree() +  geom_treescale(x=0, y=35)

legend_df <- mimicus_metadata_baps_tips %>%
  distinct(level, fill_col)
```

Add all sample metadata to tree (region, year, source of isolation)
``` {r plot tree with all metadata}
########
#plot tree and BAPS clusters 
mimicus_metadata_baps_tips$fill_col <-
  baps_colours[as.character(mimicus_metadata_baps_tips$level)]

# p + geom_hilight(node = mimicus_metadata_baps_tips$clade_node, 
#                  fill = mimicus_metadata_baps_tips$fill_col, 
#                  extendto = 0.29, alpha = 0.15) + 
p2 <- p0 + 
  geom_fruit(
  data = mimicus_metadata_baps_tips,
  geom = geom_tile,
  mapping = aes(y = id, fill = factor(level)),
  width = 0.02,
  offset = 0.05) +
  scale_fill_manual(values = baps_colours, name = "BAPS cluster") +
# add column for year
  new_scale_fill() +
  geom_fruit(
    data = mimicus_metadata_baps_tips,
    geom = geom_tile,
    mapping = aes(y = id, fill = as.numeric(year)),
    width = 0.02,
    offset = 0.08
  ) +
  scale_fill_continuous(low="thistle2", high="darkred",
                      na.value="white", guide = "colorbar", name = "Year") +
  guides(file = guide_colorbar(order = 2,
                               label.theme = element_text(angle = 90))) +
# add column for location
  new_scale_fill() +
  geom_fruit(
    data = mimicus_metadata_baps_tips,
    geom = geom_tile,
    mapping = aes(y = id, fill = loc),
    width = 0.02,
    offset = 0.08) +
  scale_fill_brewer(palette = "Set2", name = "Location", guide = guide_legend(order = 3)) +
# add column for source of isolation
  new_scale_fill() +
  geom_fruit(
    data = mimicus_metadata_baps_tips,
    geom = geom_tile,
    mapping = aes(y = id, fill = source2),
    width = 0.02,
    offset = 0.08
  ) +
  scale_fill_brewer(palette = "Set1", name = "Source", guide = guide_legend(order = 4)) +
# mark tips from this study
  geom_point(
    data = mimicus_metadata_baps_tips %>% filter(study == "this_study"),
    aes(x = xcoord, y = ycoord),
    shape = 19,   # star
    size = 3,
    color = "blue"
  ) 

p2
```

Add presence/absence of AMR and virulence genes to tree 
``` {r plot AMR and virulence genes}

mimicus_vfdb_long$gene <- factor(mimicus_vfdb_long$gene, levels = unique(mimicus_vfdb_long$gene))

#### add presence/ absence of vf genes
p3 <- p2 + new_scale_fill() +
  geom_fruit(
    data = mimicus_vfdb_long, 
    geom = geom_tile,
    colour = "gray",
    mapping = aes(x = gene, y = id, fill = presence),
    offset = 0.1, 
    pwidth = 1,
    axis.params=list(axis="x",
                     text.angle = 90,
                     text.size = 4,
                     line.size = 0,
                     hjust = 1   
                     )) + 
    scale_fill_manual(values=c("#f5af4d", "#1a318b"), name = "VF", guide = guide_legend(order = 5)) + 
    guides(
    fill = guide_legend(nrow = 4, byrow = TRUE)  # number of rows in the legend keys
  ) + new_scale_fill() +
#### add presence/ absence of amr genes
  geom_fruit(
    data = mimicus_card_long, 
    geom = geom_tile,
    colour = "gray",
    mapping = aes(x = gene, y = id, fill = presence),
    offset = 0.1,
    pwidth = 0.1,
    axis.params=list(axis="x",
                     text.angle = 90,
                     text.size = 4,
                     line.size = 0,
                     hjust = 1   
                     )) + 
    scale_fill_manual(values=c("#f5af4d", "#1a318b"), name = "AMR", guide = guide_legend(order = 6)) + 
  theme(legend.position = "bottom",
     legend.direction = "horizontal",
     legend.box = "horizontal") + 
ylim(-20, 165)


p3
```

Generate gene maps and synteny plots for cholera toxin phage found in _V. mimicus_ genomes
``` {r plot gene maps and synteny links for ctx phage}
## install version of ggplot2 compatible with gggenomes
remotes::install_version("ggplot2", "3.5.2", repos = "http://cran.us.r-project.org")
library(gggenomes)

### seqs 
ctx_mim_fna <- read_seqs("mimicus_ctx_all.fasta")

### genes
ctx_mim_gff1 <- read_feats("mimicus_ctx_all_half1.gff3")
ctx_mim_gff2 <- read_feats("mimicus_ctx_all_half2.gff3")
ctx_mim_gff <- bind_rows(ctx_mim_gff1, ctx_mim_gff2)

ctx_mim_gff_norm <- ctx_mim_gff %>%
  group_by(file_id, seq_id) %>%              # normalize separately for each sequence
  mutate(
    offset = min(start),                     # find the first coordinate
    start = start - offset + 1,               # shift start
    end   = end   - offset + 1                # shift end
  ) %>%
  ungroup() %>%
  select(-offset)


ctx_mim_gff_norm$file_id <- c("mimicus_ctx_all")

### links
ctx_mim_tbl <- read_table("ctx_blast_all.out")
ctx_mim_links <- tibble::tibble(
  seq_id = c(ctx_mim_tbl$seq_id),
  start = c(ctx_mim_tbl$start), 
  end = (c(ctx_mim_tbl$end)), 
  seq_id2 = c(ctx_mim_tbl$seq_id2),
  start2 = c(ctx_mim_tbl$start2),
  end2 = c(ctx_mim_tbl$end2),
  percent_identity = c(ctx_mim_tbl$pident)
)

### ctx phi genes colours for plotting 
colours_ctx <- c(
  "ace" = "#FFEC9D", 
  "zot" = "gold",
  "cep" = "#B9DBF1", 
  
  "ctxA" = "#FF9898",
  "ctxB" = "#D9636C",
  
  "nicK" = "#E6EE9C",
  
  "rstA" = "#E6EE9C",
  "rstB" = "#C0CA33",
  "rstB2" = "#C0CA33",
  "rstC" = "#C0CA33",
  "rstR" = "#9E9D24") 

### plot gene maps and synteny links
plot_ctx <- gggenomes(
    genes = ctx_mim_gff_norm, 
    seqs = ctx_mim_fna,
    links = ctx_mim_links
) +
  geom_seq() +
  # First fill scale for links
  geom_link(aes(fill = percent_identity), stat = "identity", colour = NA) +
  scale_fill_gradient2(low = "#ff8200", midpoint = 97, mid = "#f6eb26", high = "#00008b") + 
  ggnewscale::new_scale_fill() +
  # Second fill scale for genes
  geom_gene(aes(fill = gene), size = 8) +
  scale_fill_manual(values = colours_ctx, na.value="#FFFEEA") +
  geom_bin_label(hjust = 1, size = 5)

# plot all in same orientation 
plot_ctx_flip <- plot_ctx %>%
  sync()

plot_ctx_flip2 <- plot_ctx_flip$data$feats$genes

# align by gene ace
ace <- plot_ctx_flip2 %>%
  filter(gene == "ace") %>%
  group_by(bin_id) %>%
  slice_head(n = 1)

ctx_gggenomes <- plot_ctx_flip %>%
  gggenomes::shift(all_of(ace$seq_id), by = -ace$x) 

# order by phylogeny 
ctx_gggenomes_ordered <- ctx_gggenomes %>% gggenomes::pick("GCA_000175995.1", "GCA_963861715.1", "GCA_001471395.2", "GCA_963870535.1", "GCA_000222145.1", "GCA_963861235.1", "GCA_041015405.1", "GCA_041016145.1", "GCA_041015965.1", "GCA_041016025.1", "GCA_041015365.1", "GCA_963886345.1", "GCA_009764005.1", "GCA_041015925.1", "GCA_041015885.1", "GCA_963889215.1", "GCA_014525095.1", "GCA_041015545.1", "GCA_009665195.1", "GCA_963886145.1", "GCA_041015705.1", "GCA_041016005.1")

ctx_gggenomes_ordered

```


Generate gene maps and synteny plots for TCP operon found in _V. mimicus_ genomes
``` {r plot gene maps and synteny links for tcp operon}
#read fasta 
vpi1_mim_fna <- read_seqs("vpi-1_region_all.fasta")

#remove sequences with overlapping gene annotations 
vpi1_mim_fna <- vpi1_mim_fna[!grepl("GCA_001471395.2", vpi1_mim_fna$seq_id),]
vpi1_mim_fna <- vpi1_mim_fna[!grepl("GCA_963861715.1", vpi1_mim_fna$seq_id),]
vpi1_mim_fna <- vpi1_mim_fna[!grepl("GCA_041015705.1", vpi1_mim_fna$seq_id),]

#read gffs and merge, normalise 
vpi1_mim_gff1 <- read_feats("vpi-1_gffs_n1.gff3")
vpi1_mim_gff1[vpi1_mim_gff1$seq_id == "9",]$seq_id = "48638_1#152"
vpi1_mim_gff2 <- read_feats("vpi-1_gffs_n2.gff3")
vpi1_mim_gff3 <- read_feats("vpi-1_gffs_n3.gff3")
vpi1_mim_gff4 <- read_feats("vpi-1_gffs_n4.gff3")


vpi1_mim_gff <- bind_rows(vpi1_mim_gff1, vpi1_mim_gff2, vpi1_mim_gff3, vpi1_mim_gff4)

vpi1_mim_gff_norm <- vpi1_mim_gff %>%
  group_by(file_id, seq_id) %>%              # normalize separately for each sequence
  mutate(
    offset = min(start),                     # find the first coordinate
    start = start - offset + 1,               # shift start
    end   = end   - offset + 1                # shift end
  ) %>%
  ungroup() %>%
  select(-offset)

### links
vpi1_mim_tbl <- read_table("vpi-1_blast_all_v_all.out")

vpi1_mim_links <- tibble::tibble(
  seq_id = c(vpi1_mim_tbl$seq_id),
  start = c(vpi1_mim_tbl$start), 
  end = (c(vpi1_mim_tbl$end)), 
  seq_id2 = c(vpi1_mim_tbl$seq_id2),
  start2 = c(vpi1_mim_tbl$start2),
  end2 = c(vpi1_mim_tbl$end2),
  percent_identity = c(vpi1_mim_tbl$pident)
)

#####
#### plot colours 

colours <- c(
  "acfA" = "#B4D9CC", 
  "acfB" = "#89C0B6", 
  "acfC" = "#448C8A",
  "acfD" = "#235D72",
  
  "tcpA" = "#ADB17D",
  "tcpP" = "#767676",
  "tcpH" = "#FFB547",
  "tcpB" = "#800000",
  "tcpQ" = "#5B8FA8",
  "tcpC" = "#D49464",
  "tcpR" = "#B1746F",
  "tcpD" = "#8A8B79",
  "tcpS" = "#725663",
  "tcpT" = "#919C4C",
  "tcpE" = "#9C9EDE",
  "tcpF" = "#FD8F24",
  "tcpN" = "#F5C04A",
  "tcpJ" = "#E68C7C",
  "ssrA" = "#FF5A5A",
  
  "NA" = "#FFFEEA",
  
  "aldA" = "#F3CBD3",
  "nlpD" = "#EAA9BD",
  "tagA" = "#DD88AC",
  "tarA" = "#CA699D",
  "tpx" = "#B14D8E",
  "yckC" = "#91357D") 
#####

### plot 
plot_vpi1 <- gggenomes(genes = vpi1_mim_gff_norm, 
          seqs = vpi1_mim_fna, 
          links = vpi1_mim_links) + 
  geom_seq() +
  geom_link(aes(fill = percent_identity), stat = "identity", colour = NA) +
  scale_fill_gradient2(low = "#ff8200", midpoint = 98, mid = "#f6eb26", high = "#00008b") +
  ggnewscale::new_scale_fill() +
  geom_gene(aes(fill = gene), size = 8) +
  scale_fill_manual(values = colours, na.value="#FFFEEA") + 
  #geom_gene_tag(aes(label = gene), vjust = -2, size = 3) +
  geom_bin_label(hjust = 1, size = 5)


plot_vpi1_flip <- plot_vpi1 %>%
  sync()

plot_vpi1_flip2 <- plot_vpi1_flip$data$feats$genes

tcpB <- plot_vpi1_flip2 %>%
  filter(gene == "tcpB") %>%
  group_by(bin_id) %>%
  slice_head(n = 1)

tcp_gggenomes <- plot_vpi1_flip %>%
  gggenomes::shift(all_of(tcpB$seq_id), by = -tcpB$x)  

tcp_gggenomes_ordered <- tcp_gggenomes %>% gggenomes::pick("GCA_036553415.1", "48638_1#152", "GCA_963870535.1", "GCA_000736955.1", "GCA_000175995.1", "GCA_000222145.1", "GCA_963861235.1", "GCA_041016145.1", "GCA_041016025.1", "GCA_963886345.1", "GCA_009764005.1", "GCA_041015885.1", "GCA_009665195.1", "GCA_963886145.1", "GCA_041015545.1")

tcp_gggenomes_ordered               
```